\documentclass{article}
\usepackage{graphicx}

\title{File Transfer over TCP/IP}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\section{Protocol Design}
The protocol is designed for a simple file transfer between a client and a server using TCP/IP. The client sends a file to the server, which receives and saves it. 

\subsection{Protocol Steps}
\begin{enumerate}
    \item The client connects to the server using a specified address and port.
    \item The client reads the file in chunks and sends it to the server.
    \item The server receives the data and writes it to a local file until all data is received.
\end{enumerate}

\section{System Organization}
The system consists of a server and a client. The server listens for incoming connections and handles file reception, while the client initiates the connection and sends the file.

\section{Implementation}
The implementation consists of two main components: the server and the client.

\subsection{Server Code}
\begin{verbatim}
import socket

def server_program():
    server_socket = socket.socket()
    server_socket.bind(('localhost', 5000))
    server_socket.listen(1)
    conn, address = server_socket.accept()
    print("Connection from: " + str(address))

    with open('received_file', 'wb') as f:
        print("Receiving file...")
        while True:
            data = conn.recv(1024)
            if not data:
                break
            f.write(data)
    print("File received.")
    conn.close()

if __name__ == '__main__':
    server_program()
\end{verbatim}

\subsection{Client Code}
\begin{verbatim}
import socket

def client_program():
    client_socket = socket.socket()
    client_socket.connect(('localhost', 5000))

    with open('file_to_send', 'rb') as f:
        print("Sending file...")
        data = f.read(1024)
        while data:
            client_socket.send(data)
            data = f.read(1024)
            
    print("File sent.")
    client_socket.close()

if __name__ == '__main__':
    client_program()
\end{verbatim}

\section{Roles and Responsibilities}
\begin{itemize}
    \item \textbf{Server:} Listens for incoming connections, receives file data, and saves it.
    \item \textbf{Client:} Connects to the server, reads the file, and sends data in chunks.
\end{itemize}

\end{document}